#### Бе:Могилёвская область


```{r}
ingridients %>%
filter(region == 'Могилёвская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Могилёвская область")

```


#### Бе:Минская область


```{r}
ingridients %>%
filter(region == 'Минская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Минская область")

```


#### Бе:Витебская область


```{r}
ingridients %>%
filter(region == 'Витебская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Витебская область")

```


#### Бе:Гродненская область


```{r}
ingridients %>%
filter(region == 'Гродненская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Гродненская область")

```


#### Бе:Гомельская область


```{r}
ingridients %>%
filter(region == 'Гомельская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Гомельская область")

```


#### Бе:Брестская область


```{r}
ingridients %>%
filter(region == 'Брестская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Брестская область")

```


#### Бе:Минск


```{r}
ingridients %>%
filter(region == 'Минск') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Минск")

```


#### Ка:Восточно-Казахстанская область


```{r}
ingridients %>%
filter(region == 'Восточно-Казахстанская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Восточно-Казахстанская область")

```


#### Ка:Костанайская область


```{r}
ingridients %>%
filter(region == 'Костанайская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Костанайская область")

```


#### Ка:Павлодарская область


```{r}
ingridients %>%
filter(region == 'Павлодарская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Павлодарская область")

```


#### Ка:Карагандинская область


```{r}
ingridients %>%
filter(region == 'Карагандинская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Карагандинская область")

```


#### Ка:Алма-Ата


```{r}
ingridients %>%
filter(region == 'Алма-Ата') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Алма-Ата")

```


#### Ро:Кабардино-Балкарская Республика


```{r}
ingridients %>%
filter(region == 'Кабардино-Балкарская Республика') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Кабардино-Балкарская Республика")

```


#### Ро:Республика Дагестан


```{r}
ingridients %>%
filter(region == 'Республика Дагестан') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Дагестан")

```


#### Ро:Республика Адыгея


```{r}
ingridients %>%
filter(region == 'Республика Адыгея') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Адыгея")

```


#### Ро:Республика Хакасия


```{r}
ingridients %>%
filter(region == 'Республика Хакасия') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Хакасия")

```


#### Ро:Сахалинская область


```{r}
ingridients %>%
filter(region == 'Сахалинская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Сахалинская область")

```


#### Ро:Республика Марий Эл


```{r}
ingridients %>%
filter(region == 'Республика Марий Эл') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Марий Эл")

```


#### Ро:Камчатский край


```{r}
ingridients %>%
filter(region == 'Камчатский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Камчатский край")

```


#### Ро:Севастополь


```{r}
ingridients %>%
filter(region == 'Севастополь') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Севастополь")

```


#### Ро:Костромская область


```{r}
ingridients %>%
filter(region == 'Костромская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Костромская область")

```


#### Ро:Орловская область


```{r}
ingridients %>%
filter(region == 'Орловская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Орловская область")

```


#### Ро:Амурская область


```{r}
ingridients %>%
filter(region == 'Амурская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Амурская область")

```


#### Ро:Республика Саха (Якутия)


```{r}
ingridients %>%
filter(region == 'Республика Саха (Якутия)') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Саха (Якутия)")

```


#### Ро:Липецкая область


```{r}
ingridients %>%
filter(region == 'Липецкая область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Липецкая область")

```


#### Ро:Республика Мордовия


```{r}
ingridients %>%
filter(region == 'Республика Мордовия') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Мордовия")

```


#### Ро:Калужская область


```{r}
ingridients %>%
filter(region == 'Калужская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Калужская область")

```


#### Ро:Курская область


```{r}
ingridients %>%
filter(region == 'Курская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Курская область")

```


#### Ро:Республика Бурятия


```{r}
ingridients %>%
filter(region == 'Республика Бурятия') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Бурятия")

```


#### Ро:Забайкальский край


```{r}
ingridients %>%
filter(region == 'Забайкальский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Забайкальский край")

```


#### Ро:Астраханская область


```{r}
ingridients %>%
filter(region == 'Астраханская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Астраханская область")

```


#### Ро:Ямало-Ненецкий автономный округ


```{r}
ingridients %>%
filter(region == 'Ямало-Ненецкий автономный округ') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ямало-Ненецкий автономный округ")

```


#### Ро:Псковская область


```{r}
ingridients %>%
filter(region == 'Псковская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Псковская область")

```


#### Ро:Республика Карелия


```{r}
ingridients %>%
filter(region == 'Республика Карелия') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Карелия")

```


#### Ро:Курганская область


```{r}
ingridients %>%
filter(region == 'Курганская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Курганская область")

```


#### Ро:Ульяновская область


```{r}
ingridients %>%
filter(region == 'Ульяновская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ульяновская область")

```


#### Ро:Чувашская Республика – Чувашия


```{r}
ingridients %>%
filter(region == 'Чувашская Республика – Чувашия') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Чувашская Республика – Чувашия")

```


#### Ро:Ивановская область


```{r}
ingridients %>%
filter(region == 'Ивановская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ивановская область")

```


#### Ро:Тамбовская область


```{r}
ingridients %>%
filter(region == 'Тамбовская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Тамбовская область")

```


#### Ро:Пензенская область


```{r}
ingridients %>%
filter(region == 'Пензенская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Пензенская область")

```


#### Ро:Новгородская область


```{r}
ingridients %>%
filter(region == 'Новгородская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Новгородская область")

```


#### Ро:Смоленская область


```{r}
ingridients %>%
filter(region == 'Смоленская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Смоленская область")

```


#### Ро:Калининградская область


```{r}
ingridients %>%
filter(region == 'Калининградская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Калининградская область")

```


#### Ро:Владимирская область


```{r}
ingridients %>%
filter(region == 'Владимирская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Владимирская область")

```


#### Ро:Рязанская область


```{r}
ingridients %>%
filter(region == 'Рязанская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Рязанская область")

```


#### Ро:Кировская область


```{r}
ingridients %>%
filter(region == 'Кировская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Кировская область")

```


#### Ро:Республика Коми


```{r}
ingridients %>%
filter(region == 'Республика Коми') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Коми")

```


#### Ро:Тюменская область


```{r}
ingridients %>%
filter(region == 'Тюменская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Тюменская область")

```


#### Ро:Хабаровский край


```{r}
ingridients %>%
filter(region == 'Хабаровский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Хабаровский край")

```


#### Ро:Белгородская область


```{r}
ingridients %>%
filter(region == 'Белгородская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Белгородская область")

```


#### Ро:Приморский край


```{r}
ingridients %>%
filter(region == 'Приморский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Приморский край")

```


#### Ро:Брянская область


```{r}
ingridients %>%
filter(region == 'Брянская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Брянская область")

```


#### Ро:Мурманская область


```{r}
ingridients %>%
filter(region == 'Мурманская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Мурманская область")

```


#### Ро:Республика Крым


```{r}
ingridients %>%
filter(region == 'Республика Крым') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Крым")

```


#### Ро:Тульская область


```{r}
ingridients %>%
filter(region == 'Тульская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Тульская область")

```


#### Ро:Удмуртская Республика


```{r}
ingridients %>%
filter(region == 'Удмуртская Республика') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Удмуртская Республика")

```


#### Ро:Томская область


```{r}
ingridients %>%
filter(region == 'Томская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Томская область")

```


#### Ро:Ленинградская область


```{r}
ingridients %>%
filter(region == 'Ленинградская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ленинградская область")

```


#### Ро:Иркутская область


```{r}
ingridients %>%
filter(region == 'Иркутская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Иркутская область")

```


#### Ро:Алтайский край


```{r}
ingridients %>%
filter(region == 'Алтайский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Алтайский край")

```


#### Ро:Тверская область


```{r}
ingridients %>%
filter(region == 'Тверская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Тверская область")

```


#### Ро:Ханты-Мансийский автономный округ – Югра


```{r}
ingridients %>%
filter(region == 'Ханты-Мансийский автономный округ – Югра') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ханты-Мансийский автономный округ – Югра")

```


#### Ро:Ярославская область


```{r}
ingridients %>%
filter(region == 'Ярославская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ярославская область")

```


#### Ро:Омская область


```{r}
ingridients %>%
filter(region == 'Омская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Омская область")

```


#### Ро:Кемеровская область


```{r}
ingridients %>%
filter(region == 'Кемеровская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Кемеровская область")

```


#### Ро:Вологодская область


```{r}
ingridients %>%
filter(region == 'Вологодская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Вологодская область")

```


#### Ро:Ставропольский край


```{r}
ingridients %>%
filter(region == 'Ставропольский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ставропольский край")

```


#### Ро:Архангельская область


```{r}
ingridients %>%
filter(region == 'Архангельская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Архангельская область")

```


#### Ро:Оренбургская область


```{r}
ingridients %>%
filter(region == 'Оренбургская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Оренбургская область")

```


#### Ро:Волгоградская область


```{r}
ingridients %>%
filter(region == 'Волгоградская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Волгоградская область")

```


#### Ро:Красноярский край


```{r}
ingridients %>%
filter(region == 'Красноярский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Красноярский край")

```


#### Ро:Воронежская область


```{r}
ingridients %>%
filter(region == 'Воронежская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Воронежская область")

```


#### Ро:Саратовская область


```{r}
ingridients %>%
filter(region == 'Саратовская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Саратовская область")

```


#### Ро:Республика Татарстан


```{r}
ingridients %>%
filter(region == 'Республика Татарстан') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Татарстан")

```


#### Ро:Нижегородская область


```{r}
ingridients %>%
filter(region == 'Нижегородская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Нижегородская область")

```


#### Ро:Республика Башкортостан


```{r}
ingridients %>%
filter(region == 'Республика Башкортостан') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Республика Башкортостан")

```


#### Ро:Пермский край


```{r}
ingridients %>%
filter(region == 'Пермский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Пермский край")

```


#### Ро:Новосибирская область


```{r}
ingridients %>%
filter(region == 'Новосибирская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Новосибирская область")

```


#### Ро:Краснодарский край


```{r}
ingridients %>%
filter(region == 'Краснодарский край') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Краснодарский край")

```


#### Ро:Самарская область


```{r}
ingridients %>%
filter(region == 'Самарская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Самарская область")

```


#### Ро:Ростовская область


```{r}
ingridients %>%
filter(region == 'Ростовская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Ростовская область")

```


#### Ро:Челябинская область


```{r}
ingridients %>%
filter(region == 'Челябинская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Челябинская область")

```


#### Ро:Свердловская область


```{r}
ingridients %>%
filter(region == 'Свердловская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Свердловская область")

```


#### Ро:Московская область


```{r}
ingridients %>%
filter(region == 'Московская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Московская область")

```


#### Ро:Санкт-Петербург


```{r}
ingridients %>%
filter(region == 'Санкт-Петербург') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Санкт-Петербург")

```


#### Ро:Москва


```{r}
ingridients %>%
filter(region == 'Москва') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Москва")

```


#### Ук:Черниговская область


```{r}
ingridients %>%
filter(region == 'Черниговская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Черниговская область")

```


#### Ук:Запорожская область


```{r}
ingridients %>%
filter(region == 'Запорожская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Запорожская область")

```


#### Ук:Одесская область


```{r}
ingridients %>%
filter(region == 'Одесская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Одесская область")

```


#### Ук:Луганская область


```{r}
ingridients %>%
filter(region == 'Луганская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Луганская область")

```


#### Ук:Харьковская область


```{r}
ingridients %>%
filter(region == 'Харьковская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Харьковская область")

```


#### Ук:Днепропетровская область


```{r}
ingridients %>%
filter(region == 'Днепропетровская область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Днепропетровская область")

```


#### Ук:Киев


```{r}
ingridients %>%
filter(region == 'Киев') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Киев")

```


#### Ук:Донецкая область


```{r}
ingridients %>%
filter(region == 'Донецкая область') %>%
select(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate_all(as.integer) %>% 
group_by(carrot, fresh_cucumber, pickle, egg, greens, ham, beef, sausage,  chicken, other_flesh, no_meat, onion, fresh_pea, pickled_pea, potato, mayonnaise) %>% 
mutate(n = n()) %>% 
filter(n >= 1) %>% 
select(-n) %>% 
as.data.frame()-> 
ingredients_transformed


colnames(ingredients_transformed) <- c("морковка", "свежие огурцы", "мар./сол. огурцы", "яйца", "зелень", "ветчина", "говядина", "колбаса", "курица","др. мясо/рыба","без мяса", "лук", "свежий горошек", "конс. горошек", "картошка", "майонез")


olivier_recipe_plot(ingredients_transformed, freq_max = 0, title = "Донецкая область")

```


